### 2014-10-21 fundamentals/intro.tex
breaking the cycle with cyclus

Historically, researchers create new nuclear fuel cycle simulation tools when 
existing tools are not available or not sufficiently general to calculate their 
metrics of interest with their method of choice.

Historically, the national laboratories have driven development and regulated 
the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{modeling_yacout_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}. With limited access to those tools 
and a need to customize them for research purposes, 
universities and private industry researchers ``reinvent the wheel'' by 
developing tools of their own from scratch and tailored to their own needs (e.g., 
\gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi} 
respectively).

@@

Accordingly, the \gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code
was created to provide and extensible interface to facilitate collaboration. 
The \gls{GENIUSv2} project relied on lessons-learned from an \gls{LDRD} project 
at \gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}.

The \Cyclus project, in turn, improved upon the \gls{GENIUSv2} project by 
implementing increased modularity and encapsulation.
The result is  a dynamic simulator that treats both materials and facilities 
discretely, with an architecture that permits simulations with multiple and 
variable levels of fidelity. Its agent-based framework for simulation and 
tracking of transformation and trade of resources between facilities within 
institutions and regions greatly improves upon the existing field of fuel cycle 
simulators.

>>>>

Historically, the national laboratories have driven development and regulated 
the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{modeling_yacout_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}. 
Outside of the national laboratories, researchers create new nuclear fuel cycle 
simulation tools when existing tools are not available or not sufficiently 
general to calculate their metrics of interest with their method of choice.  
With limited access to the national laboratory tools and a need to customize 
them for research purposes, universities and private industry researchers 
``reinvent the wheel'' by developing tools of their own from scratch and 
tailored to their own needs (e.g., \gls{CAFCA}\cite{guerin_benchmark_2006} and 
\gls{COSI}\cite{cosi} respectively).

@@

The \Cyclus simulator emerged from a line of tools seeking to break that cycle.  
An \gls{LDRD} project begun at \gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} sought 
to provide generic regional capability.  Based on lessons learned from 
\gls{GENIUSv1}, the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
provide more generality and an extensible interface to facilitate 
collaboration.  The \Cyclus project, in turn, improved upon the \gls{GENIUSv2} 
project by implementing increased modularity and encapsulation.  The result is  
a dynamic simulator that treats both materials and facilities discretely, with 
an architecture that permits simulations with multiple and variable levels of 
fidelity. Its agent-based framework for simulation and tracking of 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing field of fuel cycle simulators.
